---
pagetitle: "Main Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") 
  })
---

## Esimtation Results
The following plots show the regression table as well as the qq-plot, histogramm of the residuals. The model was compared to that of assuming a gaussian distribution of the dependent variable 

Scaled t distribution model
```{r masdasdasdsad analysis, echo = FALSE}
library("mgcv")
library("lubridate")
data_causal1 <- read.csv("../data/data_causal1.csv")
data_causal2 <- read.csv("../data/data_causal2.csv")
data_causal2$sales_date<-ymd(data_causal2$sales_date)
data_causal1$sales_date<-ymd(data_causal1$sales_date)
scatmodel<-bam(lprice ~s(density) + s(time) + s(pc4,bs="re") +
          wtype + construction_period + garden +
          lsize + parking + monumentalstatus + buyerpaysorfree +
          quality + population +  gdp_change + 
          accommodation_nl_change ,
          family = scat, data=data_causal1)
summary(scatmodel)
plot(scatmodel)
```
The important effect $density$ is significant, as well as $time$ and $pc4$. The majority of control variables is as well.



Gaussian distribution model
```{r descriptive anaasdadsdsdsadlysis, echo = FALSE}
gaussianmodel<-bam(lprice ~s(density) + s(time) + s(pc4,bs="re") +
          wtype + construction_period + garden +
          lsize + parking + monumentalstatus + buyerpaysorfree +
          quality + population +  gdp_change + 
          accommodation_nl_change ,
          data=data_causal1)

summary(gaussianmodel)
plot(gaussianmodel)
```

```{r descriptive analyasdasdddasdsis, echo = FALSE}
par(mfrow=c(1,2))
{qqnorm(residuals.gam(scatmodel))
lines(qqline(residuals.gam(scatmodel),col=2))}
{hist(residuals(scatmodel), freq =F)
lines(density(residuals(scatmodel)), col=2)}

{qqnorm(residuals.gam(gaussianmodel))
qqline(residuals.gam(gaussianmodel),col=2)}
{hist(residuals(gaussianmodel), freq =F)
lines(density(residuals(gaussianmodel)), col=2)}
```
One can observe that the gaussian distribution is inadequate. It 
For a robustness check the model was estimated with the data from 2009 to 2012 as well.

```{r descriptive analadaddsdasdysis, echo = FALSE}
scatmodel_robust<-bam(lprice ~s(density) + s(time) + s(pc4,bs="re") +
          wtype + construction_period + garden +
          lsize + parking + monumentalstatus + buyerpaysorfree +
          quality + population +  gdp_change + 
          accommodation_nl_change ,
          family = scat, data=data_causal2)
summary(scatmodel_robust)
plot(scatmodel_robust)
```
Thus we see the model is robust.

