---
title: "main_analysis"
author: "Rouven Schmidt"
date: "4/8/2021"
output: html_document
---

# Esimtation Results
The following plots show the regression table as well as the qq-plot, histogramm of the residuals. The model was compared to that of assuming a gaussian distribution of the dependent variable 

Scaled t distribution model
```{r descriptive analysis, child = 'descriptive_analysis.Rmd'}
scatmodel<-bam(lprice ~s(density) + s(time) + s(pc4,bs="re") +
          wtype + construction_period + garden + distance + 
          lsize + parking + monumentalstatus + buyerpaysorfree +
          quality + population +  gdp_change + hpi_groningen_change +   
          hpi_southholland_change + hpi_nordbrabant_change + 
          as.numeric(hpi_rotterdam_change) + accommodation_nl_change,
          family = scat, data=data_causal1)
summary(scatmodel)
```

```{r descriptive analysis, child = 'descriptive_analysis.Rmd'}
gaussianmodel<-bam(lprice ~s(density) + s(time) + s(pc4,bs="re") +
          wtype + construction_period + garden + distance + 
          lsize + parking + monumentalstatus + buyerpaysorfree +
          quality + population +  gdp_change + hpi_groningen_change +   
          hpi_southholland_change + hpi_nordbrabant_change + 
          as.numeric(hpi_rotterdam_change) + accommodation_nl_change,
          data=data_causal1)
```

summary(m4)

qqnorm(residuals.gam(m2))
qqline(residuals.gam(m2),col=2)
hist(residuals(m2), freq =F)
lines(density(residuals(m2)), col=2)

qqnorm(residuals.gam(m4))
qqline(residuals.gam(m4),col=2)
hist(residuals(m4), freq =F)
lines(density(residuals(m4)), col=2)