---
title: 'Econometric Game 2021 - Team Göttingen'
author: "Chris-Gabriel Islam, Jens Lichter, Alexander Ritz and Rouven Schmidt"
date: "09/04/2021"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") 
  })
---

This is a dynamic report for the Econometric Game 2021 - Team Göttingen. In the first chapter we analyze the data and justify our edits. The second chapter gives some summary statistics while the third chapter is the main component. In this chapter we develop models that answer the given research questions. The last chapter refers to our conclusions.

# Data editing

```{r data editing, child = 'data_editing.Rmd'}
```

# Descriptive Analysis

```{r descriptive analysis, child = 'descriptive_analysis.Rmd'}
```

# Statistical Model
The applied method is a general additive model (GAM). The dependent variable $log(price_i)$ with $i=1,...,n$ is assumed to follow a normal distribution. The model equation is as follows:

\[
log(price_{it}) = \beta_0 + \beta_1 wtype_{it}  + \beta_2 construction\_period_{it} + \beta_3 garden_{it} + \\
          \beta_4 size_{it} + \beta_5 parking_{it} + \beta_6 monumentalstatus_{it} + \beta_7 buyerpaysorfree_{it} + \\
          \beta_8 quality_{it} + \\
          \gamma_{t} pc4_{it} +
          f_1(denstiy_{it}) +
          f_2(time_{it})
          
\]
where, one has to consider, that the categorial variables $wtype,construction\_period, garden, parking, monumentalstatus, buyerpaysorfree$ and  $quality$ are dummy coded, thus resulting in multiple $\beta$. These are neglected for ease of notation, in the above equation. The non-linear functions $f_j$ for $j \in \{1,2\}$ are approximated using p-splines of the form: 
\[
f_j(z_j)=\sum_{l=1}^{d_j} \gamma_{jl} B_l(z_j)
\]
where $d_j$ is the number dimension of the basis used to represent the smooth.
Further, the effect of $pc4$ is modelled as a random effect with $pc4_t \sim N(0,\sigma_\gamma)$
For more details see GAM SIMON WOOD.
The model can be estimated via maximum likelihood estimation. The \textit{mgcv} package by Simon Wood was used.


```{r descriptive analysis, child = 'descriptive_analysis.Rmd'}
```

# Esimtation Results

