---
title: 'Econometric Game 2021 - Team Göttingen'
author: "Anonymous"
date: "09/04/2021"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") 
  })
---

This is a dynamic report for the Econometric Game 2021. The advantage over a normal paper is its reproducibility. This dynamic report contains all data and calculation steps in order to reproduce our results. Especially during nowadays [replication crisis](https://en.wikipedia.org/wiki/Replication_crisis), this is of uttermost importance. In the first chapter we give an introduction as well as literature overview. Then, we describe our data. Next, we explain the design and the methods we use, before presenting our results. The last chapter refers to our conclusions.


# Introduction

```{r data editing, child = 'intro.Rmd'}
```

# Data description

```{r data description, child = 'data_description.Rmd'}
```

# Methods and design

```{r data editing, child = 'methods.Rmd'}
```

```{r data editing, child = 'gis.Rmd'}
```

# Results

## Descriptive analysis

```{r descriptive analysis, child = 'descriptive_analysis.Rmd'}
```

## Causal inference

```{r descddripddddtive, child = 'main_analysis.Rmd'}
```

# Conclusion

```{r data editing, child = 'conclusion.Rmd'}
```

